---
title: "Mesocosm Paper Environmental Plots"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---
```{r, echo=FALSE, message=FALSE,  warning=FALSE}

library(ggplot2)
library(tidyverse)
library(scales)
library(dplyr)
library(vegan)
library(RColorBrewer)
library(gghighlight)
library(egg)
library(gridExtra)
```

```{r, echo=FALSE}


distenv <- read.csv("~/Desktop/PICO_all_clean.csv", header=T)

florence=distenv[366:475,]

```

###Figure showing chla, salinity and DOC after florence relative to average PICO concentrations 
```{r}

distenv2 = read.csv("~/Desktop/PICO_noHurr_clean.csv", header=TRUE)

chloro=ggplot(distenv2, aes(x = YearDay, y = Chloro))+ 
  geom_point(alpha=0.1, color="forestgreen")  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=Chloro), color="forestgreen") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  geom_smooth(data=distenv2, color="black", method="loess",span=0.2, size=0.5, level=0.95) + ylab("Chl a (mg/L)") + xlim(200, 365)

doc=ggplot(distenv2, aes(x = YearDay, y = DOC))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=DOC), color="maroon") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv2, color="black", method="loess",span=0.2, size=0.5, level=0.95) + ylab("DOC (uM)") + xlim(200, 365)

sal = ggplot(distenv2, aes(x = YearDay, y = Salinity))+ 
  geom_point(alpha=0.1, color="blue")  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=Salinity), color="blue") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  geom_smooth(data=distenv2, color="black", method="loess",span=0.2, size=0.5, level=0.95) + ylab("Salinity (PSU)") + xlim(200, 365)

svg("~/Desktop/HM_env_faceted_nohur.svg")
ggarrange( sal, chloro,doc, 
          labels = c("A", "B", "C"),
          ncol = 1, nrow = 3)

dev.off()
``` 


##Figure of FCM data over time by treatment
```{r}

hm5_meta = read.csv("~/Desktop/HM5_metadata.csv", header=T)

hmfcm = read.csv("~/Desktop/HM5_FCM_data.csv", header=T)

```



```{r}
syn = ggplot(hmfcm, aes(x = Day, y = Syn)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Log(Synechococcus)") + 
  geom_errorbar(aes(ymin=Syn-SynSD, ymax=Syn+SynSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=11),
          axis.text.y = element_text(size=11))

peuks = ggplot(hmfcm, aes(x = Day, y = Peuks)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Log(Picoeukaryotes)") + 
  geom_errorbar(aes(ymin=Peuks-PeuksSD, ymax=Peuks+PeuksSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=11),
          axis.text.y = element_text(size=11))

cyano = ggplot(hmfcm, aes(x = Day, y = Picocyano)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Log(Picocyanobacteria)") + 
  geom_errorbar(aes(ymin=Picocyano-PicocyanoSD, ymax=Picocyano+PicocyanoSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=11),
          axis.text.y = element_text(size=11))

bac = ggplot(hmfcm, aes(x = Day, y = Bacteria)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Log(Bacteria)") + 
  geom_errorbar(aes(ymin=Bacteria-BacteriaSD, ymax=Bacteria+BacteriaSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=11),
          axis.text.y = element_text(size=11))
```

```{r}
library(ggpubr)
svg("~/Desktop/HM5_FCM.svg", height=8, width=14)
ggarrange( syn, cyano,peuks,bac, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2, common.legend=TRUE)

dev.off()

```

##Line plots of chlorophyll, doc, temp, and BOD over time
```{r}

hmenv = read.csv("~/Desktop/HM5_env.csv", header=T)

```

```{r}
chl = ggplot(hmenv, aes(x = Day, y = ChlAvg)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Chla") + 
  geom_errorbar(aes(ymin=ChlAvg-ChlSD, ymax=ChlAvg+ChlSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=11),
          axis.text.y = element_text(size=11))

svg("~/Desktop/HM5_chlorophyll.svg", height=5, width=10)
chl
dev.off()

```

```{r}


bod = hmenv[c(1:3, 10:12, 16:18),]

```

```{r}
chl = ggplot(hmenv, aes(x = Day, y = ChlAvg)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Chla") + 
  geom_errorbar(aes(ymin=ChlAvg-ChlSD, ymax=ChlAvg+ChlSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=12))

doc = ggplot(bod, aes(x = Day, y = DOCavg)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("DOC") + 
  geom_errorbar(aes(ymin=DOCavg-DOCsd, ymax=DOCavg+DOCsd), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=12))

resp = ggplot(bod, aes(x = Day, y = ResAvg)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Repiration") + 
  geom_errorbar(aes(ymin=ResAvg-ResSD, ymax=ResAvg+ResSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=12))

grossphoto = ggplot(bod, aes(x = Day, y = PhotoAvg)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Photosynthesis") + 
  geom_errorbar(aes(ymin=PhotoAvg-PhotoSD, ymax=PhotoAvg+PhotoSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=12))

netprod = ggplot(bod, aes(x = Day, y = ProdAvg)) + 
  geom_line(aes(color = Treatment))+
  scale_color_manual(values = c("darkred", "blue", "forestgreen")) +
   geom_point()+ ylab("Productivity") + 
  geom_errorbar(aes(ymin=ProdAvg-ProdSD, ymax=ProdAvg+ProdSD), width=.1,
                 position=position_dodge(0.05))+ theme_bw()+
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"), axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=12))


```

```{r}
library(ggpubr)
svg("~/Desktop/HM5_env.svg", height=12, width=14)
ggarrange(chl, doc,resp,grossphoto, netprod,
          labels = c("A", "B", "C", "D", "E"),
          ncol = 2, nrow = 3, common.legend=TRUE, legend="bottom")

dev.off()

```










#Code for testing aesthetics
```{r}

ggplot(distenv, aes(x = YearDay, y = Temp))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=Temp), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)
```


```{r}


temp = ggplot(distenv, aes(x = YearDay, y = Temp))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=Temp), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)

ph=ggplot(distenv, aes(x = YearDay, y = pH))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=pH), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)

sal = ggplot(distenv, aes(x = YearDay, y = Salinity))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=Salinity), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)

dic=ggplot(distenv, aes(x = YearDay, y = DIC))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=DIC), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)

amm=ggplot(distenv, aes(x = YearDay, y = NH4))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=NH4), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)



sil=ggplot(distenv, aes(x = YearDay, y = SiO4))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=SiO4), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)


chloro=ggplot(distenv, aes(x = YearDay, y = Chloro))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=Chloro), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)

bact = ggplot(distenv, aes(x = YearDay, y = LogBacteriaAvg))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=LogBacteriaAvg), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)


cyano = ggplot(distenv, aes(x = YearDay, y = LogpicocyanobacteriaAvg))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=LogpicocyanobacteriaAvg), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)
  


euk = ggplot(distenv, aes(x = YearDay, y = LogpicophotoeukaryotesAvg))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=LogpicophotoeukaryotesAvg), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)


syn=ggplot(distenv, aes(x = YearDay, y = LogSynechococcusAvg))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=LogSynechococcusAvg), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)

doc=ggplot(distenv, aes(x = YearDay, y = DOC))+ 
  geom_point(alpha=0.1)  + gghighlight(PICONumber==869, label_key = PICONumber)+theme_bw()+
  geom_line(data=florence, aes(x=YearDay, y=DOC), color="red") + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  geom_smooth(data=distenv, color="black", method="loess",span=0.2, size=0.5, level=0.95)
 
```

```{r}

svg("~/Desktop/HM_environment_1.svg", width = 14, height = 24)
ggarrange(temp, ph, sal, dic, amm, sil, chloro, bact, cyano, euk, syn,doc, 
          labels = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L"),
          ncol = 2, nrow = 6)


dev.off()

```




```{r}

svg("~/Desktop/HM_sal_doc.svg", height=4, width=12)

ggarrange(sal,doc, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)


dev.off()

```

#Salinity and DOC plot with LOESS smoothing
```{r}


ggplot(florence, aes(x=YearDay)) +
  geom_line( aes(y=Salinity*10), color="blue") +
  geom_line( aes(y=DOC), color="forestgreen") + 
  scale_y_continuous(name = "DOC (uM)",sec.axis = sec_axis(~./10, name="Salinity (PSU"))+ 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+theme_bw() +
  geom_smooth(data=distenv, aes(x=YearDay, y=DOC), color="black", method="loess",span=0.2, size=0.5, level=0.95)+
  geom_smooth(data=distenv, aes(x=YearDay, y=Salinity*10), color="black", method="loess",span=0.2, size=0.5, level=0.95) + theme(panel.grid=element_blank())


```

#Salinity and DOC plot with points
```{r}


ggplot(florence, aes(x=YearDay)) +
  geom_line( aes(y=Salinity*10), color="blue") +
  geom_line( aes(y=DOC), color="forestgreen") + 
  scale_y_continuous(name = "DOC (uM)",sec.axis = sec_axis(~./10, name="Salinity (PSU"))+ 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+theme_bw() +
  geom_point(data=distenv, aes(x=YearDay, y=DOC), alpha=0.1, color="forestgreen")+
  geom_point(data=distenv, aes(x=YearDay, y=Salinity*10), alpha=0.1, color="blue") + theme(panel.grid=element_blank()) 


```

```{r}


ggplot(florence, aes(x=YearDay)) +
  geom_line( aes(y=NH4), color="purple") +
  geom_line( aes(y=Chloro*1000), color="green") + 
  scale_y_continuous(name = "NH4 (uM)",sec.axis = sec_axis(~./1000, name="Chlorophyll"))+ 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+theme_bw() +
  geom_point(data=distenv, aes(x=YearDay, y=NH4), alpha=0.1, color="purple")+
  geom_point(data=distenv, aes(x=YearDay, y=Chloro*1000), alpha=0.1, color="green") + theme(panel.grid=element_blank()) 


```



###Making plot with three axes
```{r}
##Define each axis dataset

time = florence$YearDay

chl = florence$Chloro

sal = florence$Salinity

doc = florence$DOC

```

```{r}
my_col1 = "#228B22"
my_col_alpha1 <- adjustcolor(my_col1, alpha.f = 0.2)

my_col2 = "#000000"
my_col_alpha2 <- adjustcolor(my_col2, alpha.f = 0.2)

my_col3 = "#0000FF"
my_col_alpha3 <- adjustcolor(my_col3, alpha.f = 0.2)

```


```{r}

svg("~/Desktop/HM_env3_zoom.svg", width=20, height=12)
#Define Margins. The trick is to use give as much space possible on the left margin (second value)
par(mar=c(8, 12, 4, 4) + 0.1)


#Plot the first time series. Notice that you don’t have to draw the axis nor the labels


plot(time, chl, axes=F, ylim=c(0,max(chl)), xlab="", ylab="",type="l",col="forestgreen", main="",xlim=c(180,365),lwd=3)
points(distenv$YearDay,distenv$Chloro, pch=20, col=my_col_alpha1, cex=0.5)
axis(2, ylim=c(0,max(chl)),col="forestgreen",lwd=2)
mtext(2,text="Chlorophyll a (mg/L)",line=2)




#Plot the second time series. The command par(new=T) is handy here. If you just need to plot two timeseries, you could also use the right vertical axis as well. In that case you have to substitute “2” with “4” in the functions axis() and mtext(). Notice that in both functions lines is increased so that the new axis and its label is placed to the left of the first one. You don’t need to increase the value if you use the right vertical axis.


par(new=T)
plot(time, doc, axes=F, ylim=c(0,max(doc)), xlab="", ylab="", 
type="l",lty=1, main="",xlim=c(180,365),lwd=3, col="black")
axis(2, ylim=c(0,max(doc)),lwd=2,line=3.5)
points(distenv$YearDay,distenv$DOC, pch=20, col=my_col_alpha2, cex=0.5)
mtext(2,text="DOC (uM)",line=5.5)


#Plot the third time series. Again the line parameter are both further increased.


par(new=T)
plot(time, sal, axes=F, ylim=c(0,max(sal)), xlab="", ylab="", 
type="l",lty=1, main="",xlim=c(180,365),lwd=3, col="blue")
axis(2, ylim=c(0,max(sal)),lwd=2,line=7, col="blue")
points(distenv$YearDay,distenv$Salinity, pch=20, col=my_col_alpha3, cex=0.5)
mtext(2,text="Salinity (PSU)",line=9)


#We can now draw the X-axis, which is of course shared by all the three time-series.


axis(1,pretty(range(time),10))
mtext("Year Day",side=1,col="black",line=2)


dev.off()
#And then plot the legend.


#legend(x=20,y=12,legend=c("Chlorophyll a (mg/L)","DOC (uM)", "Salinity (PSU)"),lty=c(1,2,3))

```

###statistical test for difference between dilution and control on day 5 for FCM counts
```{r}

phyto = read.csv("~/Desktop/HM5_phyto_day5.csv", header=T)

dil = subset(phyto, Treatment=="Dilution")
dom = subset(phyto, Treatment=="DOM")
con = subset(phyto, Treatment=="Control")

```

```{r}

wilcox.test(dil$PicoCyano, con$PicoCyano, alternative="less")

wilcox.test(dil$PicoEuks, con$PicoEuks,  alternative="less")

wilcox.test(dil$Syn, con$Syn, alternative="less")

wilcox.test(dil$Bacteria,con$Bacteria,  alternative="less")

```
```{r}

hist(phyto$Syn)
hist(phyto$PicoCyano)
hist(phyto$PicoEuks)

```
